---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dubioustests

*dubioustests* is a testing package for lazy typers with parentheses-phobia.

It essentially proposes shorthands for *testthat* functions, using a syntax
powered by the *doubt* package, hence its name.

Install with :

```{r, eval = FALSE}
remotes::install_github("moodymudskipper/dubioustests")
```

## Examples

Let's attach both *dubioustests* and *testthat* and review sets of equivalent calls.

```{r}
library(testthat)
library(dubioustests, warn.conflicts = FALSE)
```

Test if a value is `TRUE` :

```{r}
expect_true(is.numeric(2))
?~ is.numeric(2)
```

Test if two values are equal using `all.equal()`

```{r}
expect_equal(tan(pi/4), 1)
?e~ tan(pi/4) ? 1
```

Test if two values are identical using `identical()`

```{r, error = TRUE}
expect_identical(tan(pi/4), 1)
?i~ tan(pi/4) ? 1
```

We can also use the infix notation and write `tan(pi/4) ?i~ 1` instead of
`?i~ tan(pi/4) ? 1`

## Wrap it up with `%?%`

`%?%` is `testthat::test_that()` but the description text comes first and we don't
need parentheses anymore.

Putting  everything together we get :

```{r}
"test that my functions work" %?% {
  ?~  is.numeric(2)
  ?e~ tan(pi/4) ? 1
}
```


## Other aliases ?

The package doesn't propose other aliases for *testthat* functions at the moment.

In many case the `?~` or `?e~` shorthands do the job just fine though. The two
following expressions would only differ by the error message they would generate
but they're  explicit either way.

```{r, error = TRUE}
test_that("a few things work as they should", {
  expect_length(4:6, 4)
  expect_gt(4, 5)
  expect_match("foobar","^bar")
})

"a few things work as they should" %?% {
  ?~ length(4:6) == 4
  ?~ 4 > 5
  ?~ grepl("^bar","foobar")
}
```

And if needed we can easily define new dubious aliases :

```{r, error = TRUE}
`?len~` <- expect_length
`?err~` <- expect_error
?len~ 4:6 ? 4
?err~ stop("foo error")
?err~ stop("foo error") ? "^foo"
?err~ stop("foo error") ? "^bar"
```
