---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dubioustests

*dubioustests* is a testing package for lazy typers who don't like parentheses.

It essentially proposes shorthands for *testthat* functions, using a syntax
powered by the *doubt* package, hence its name.

Install with :

```{r, eval = FALSE}
remotes::install_github("moodymudskipper/dubioustests")
```

## Examples

Let's attach both *dubioustests* and *testthat* and review sets of equivalent calls.

```{r}
library(testthat)
library(dubioustests, warn.conflicts = FALSE)
```

Test if a value is `TRUE` :

```{r}
expect_true(is.numeric(2))
?~ is.numeric(2)
```

Test if two values are equal using `all.equal()`

```{r}
expect_equal(tan(pi/4), 1)
?e~ tan(pi/4) ? 1
```

Test if two values are identical using `identical()`

```{r, error = TRUE}
expect_identical(tan(pi/4), 1)
?i~ tan(pi/4) ? 1
```

We can also use the infix notation and write `tan(pi/4) ?i~ 1` instead of
`?i~ tan(pi/4) ? 1`

## Wrap it up with `%?%`

`%?%` is `testthat::test_that()`. The nice thing about it is we don't need brackets
anymore and the description text comes first.

Putting  everything together we get :

```{r}
"test that my functions work" %?% {
  ?~ is.numeric(2)
  ?e~ tan(pi/4) ? 1
}
```


## Other aliases ?

The package doesn't propose other aliases for *testthat* functions at the moment.

In many case the `?~` or `?e~` shorthands do the job just fine though.

```{r}
expect_length(4:6, 3)
?~ length(4:6) == 3
expect_gt(4, 3)
?~ 4 > 3
```

And if needed we can easily define a new alias:

```{r, error = TRUE}
`?len~` <- expect_length
`?err~` <- expect_error
?len~ 4:6 ? 4
?err~ stop("foo error")
?err~ stop("foo error") ? "^foo"
?err~ stop("foo error") ? "^bar"
```
